Evaluating infectious disease forecasts \\ with allocation scoring rules

### 2024-08-01 alloscore_manuscript/manuscript.tex
fix legend.pos->legend.position in metrics-over-time (fig4) components
sensitivity analysis  and discussion

@@

AS was computed for a range of $K$ from 200 to 60,000 for forecasts made on December 20, 2020 predicting levels of
hospitalizations on January 3, 2021 as well as for the \texttt{per-capita} allocation (Figure \ref{fig:multi-k}A). These
calculations highlight that AS was highest at at values of $K$ near the observed nationwide total hospital admissions of
19,581 that day. Model ranks by AS were fairly stable across all $K$, and there appears
to be an substantial interval around the observed value over which ranks are constant.

@@

>>>>

\subsection{Sensitivity of allocation score to values of K}
\label{sec:sensitivity}

To assess the sensitivity of AS to choice of $K$, AS was computed for a range of $K$ from 200 to 60,000 for forecasts made on December 20, 2020 predicting levels of hospitalizations on January 3, 2021 as well as for the \texttt{per-capita} allocation (Figure \ref{fig:multi-k}A). These calculations highlight that AS was highest at at values of $K$ near the observed nationwide total hospital admissions of 19,581 that day. Model ranks by AS were fairly stable across all $K$, and there appears to be an substantial interval around the observed value over which ranks are constant.

@@

@@

Additionally, during an epidemic, public health decision makers may be faced with an ongoing series of decision over time in response to changes in conditions such as resource availability or the current allocations of resources. The AS presented here looks at a single snapshot in time  and ignores many of the complexities related to adjusting existing allocations. The example presented in section \ref{sec:application} is based on a prospective estimate of bed availability, but one could use observed total resource availability to derive an
